The Power of Dependent Reflection

### 2021-07-05 paper.tex
Some additions and changes to the abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  This paper proposes a novel tecnhique to write correct by construction
  programs in languages that do not have built-in verification
  capabilities.  This is achieved in three steps.  Firstly, we
  shallowly embed the language (or its subset) into a
  dependently-typed system.  Secondly, we write a program
  in that embedding, and we use dependent types to guarantee
  correctness properties of interest.  Thirdly, we
  translate the embedded program back into the original language,
  so that it can be used by the existing compilers and tools.

  The main insight of the paper is the observation that de\-pen\-den\-tly-typed
  languages that are equipped with reflection mecahnisms make it possible
  to expres all the three steps in a single language.  Essentially,
  this allows us to express programs, its formal properties and
  compilers hand-in-hand, offering a lot of flexibility to programmers.

  To demonstrate the approach precisely, we embed a subset of
  the PostScript language in Agda.  We explain all the three
  steps, illustrating them with several short examples.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}

  Dependent types can be used to ensure programs are correct by construction,
  but they are not available in most
  languages and adding them to an existing language is a difficult task.
  This paper proposes a novel technique to write correct-by-construction
  programs in languages without built-in verification
  capabilities.  This is achieved in three steps.  Firstly, we
  give a shallow embedding of the language (or a subset) into a
  dependently typed language.  Secondly, we write a program
  in that embedding, and we use dependent types to guarantee
  correctness properties of interest.  Thirdly, we
  translate the embedded program back into the original language,
  so that it can be used by the existing compilers and tools.

  Our main insight is that it is possible to
  express all three steps in a single language, as long as it supports
  both dependent types and reflection. Essentially,
  this allows us to express a program, its formal properties, and
  a compiler for it hand-in-hand, offering a lot of flexibility to programmers.
  We demonstrate this three-step approach by embedding a subset of
  the PostScript language in Agda, and illustrating it with several short examples.
  Thus we use the power of reflection to bring the benefits of dependent types to languages
  that had to go without them so far.
